Managing variability in software systems

### 2021-06-04 Paper.tex
remove unused references

Decision models can be represented in different ways, broadly used approaches are flat lists or tables of decisions which also includes their dependencies. In decision modeling hierarchy is a secondary aspect, because there are no uniform rules to describe hierarchy.\cite{b6}\\

Same as feature modeling, decision modeling has been expanded over time to enable the application coverage of DM to be almost the same as FM.\cite{b6}\\

@@

As mentioned in \cite{b4} the currently existing methods also have their limitations. 
\begin{itemize}
\item \textit{Guaranteed correctness and consistency}. Authors have to urge for verification and consistency checking.\\
\item \textit{Performance overheads} are difficult to model.\\
\item \textit{Runtime upgradability} and the process of switching features is sometimes necessary.\\
\item \textit{Lack of support for security needs} can be a factor which limits the use of feature modeling.\\
\item \textit{Poor user-friendliness} can be introduced by poor handling of variability, which decreases the usability of a system.\\
\end{itemize}

@@

\begin{thebibliography}{00}
\bibitem{b1} S. Apel, D. Batory, C. Kästner and G. Saake, "Software Product Lines. In: Feature-Oriented Software Product Lines", Berlin Heidelberg, Springer (2013)
\bibitem{b2} J. van Gurp, J. Bosch and M. Svahnberg, "On the notion of variability in software product lines," Proceedings Working IEEE/IFIP Conference on Software Architecture", Amsterdam, Netherlands, 2001
\bibitem{b3} F. Bachmann, L. Bass, "Managing Variability in Software Architectures", Carnegie Mellon University (2001)
\bibitem{b4} M. Galster, D. Weyns, D. Tofan, M. Bartosz, P. Avgeriou, "Variability in Software Systems—A Systematic Literature Review", IEEE Transactions on Software Engineering (2014)
\bibitem{b5} T. Berger, J.-P. Steghöfer, T. Ziadi, J. Robin, and J. Martinez, "The state of adoption and the challenges of systematic variability management in industry", Empirical Software Engineering, vol. 25, 2020
\bibitem{b6}
K. Czarnecki, P. Grünbacher, R. Rabiser, K. Schmid., and A.
Wasowski, “Cool features and tough decisions: a comparison of
variability modeling approaches”, Proc. of the \textit{Sixth international
workshop on variability modeling of software-intensive systems
(VaMoS '12)}, ACM, Jan 2012
\bibitem{b7}
Software Productivity Consortium Services Corporation,
Technical Report SPC-92019-CMC. \textit{Reuse-Driven Software
Processes Guidebook}, Version 02.00.03, 1993.
\bibitem{b8} K. C. Kang, S. Cohen, J. Hess, W. Novak, and S. Peterson,	 "Feature oriented domain analysis (FODA) feasibility study", Technical Report CMU/SEI-90-TR-21, Software Engineering Institute, Carnegie Mellon University, Pittburgh, PA, USA, 1990
\bibitem{b9} A. Metzger, and K. Pohl, "Software product line engineering and variability management: Achievements and challenges," \textit{Proc. of the Future of Software Engineering (FOSE 2014)}, ACM, 2014, pp. 70-84, doi:10.1145/2593882.2593888.
\bibitem{b10} M. Riebisch, K. Böllert, D. Streitferdt, and I. Philippow, "Extending Feature Diagrams with UML Multiplicities", \textit{6th World Conference on Integrated Design \& Process Technology (IDPT2002)}, vol. 23, 2002
\bibitem{b11} K. Schmid, R. Rabiser, P. Grünbacher, "A comparison of decision modeling approaches in product lines", Proc. of the \textit{Fifth international
workshop on variability modeling of software-intensive systems
(VaMoS '11)}, ACM, Jan 2011
\end{thebibliography}

>>>>

Decision models can be represented in different ways, broadly used approaches are flat lists or tables of decisions which also includes their dependencies. In decision modeling hierarchy is a secondary aspect, because there are no uniform rules to describe hierarchy.
Same as feature modeling, decision modeling has been expanded over time to enable the application coverage of DM to be almost the same as FM.\cite{b6}\\

@@

As mentioned in \cite{b4} the currently existing methods also have their limitations. 
\begin{itemize}
\item \textit{Guaranteed correctness and consistency}. Authors have to urge for verification and consistency checking.
\item \textit{Performance overheads} are difficult to model.
\item \textit{Runtime upgradability} and the process of switching features is sometimes necessary.
\item \textit{Lack of support for security needs} can be a factor which limits the use of feature modeling.
\item \textit{Poor user-friendliness} can be introduced by poor handling of variability, which decreases the usability of a system.
\end{itemize}

@@

\begin{thebibliography}{00}
\bibitem{b2} J. van Gurp, J. Bosch and M. Svahnberg, "On the notion of variability in software product lines," Proceedings Working IEEE/IFIP Conference on Software Architecture", Amsterdam, Netherlands, 2001
\bibitem{b3} F. Bachmann, L. Bass, "Managing Variability in Software Architectures", Carnegie Mellon University (2001)
\bibitem{b4} M. Galster, D. Weyns, D. Tofan, M. Bartosz, P. Avgeriou, "Variability in Software Systems—A Systematic Literature Review", IEEE Transactions on Software Engineering (2014)
\bibitem{b5} T. Berger, J.-P. Steghöfer, T. Ziadi, J. Robin, and J. Martinez, "The state of adoption and the challenges of systematic variability management in industry", Empirical Software Engineering, vol. 25, 2020
\bibitem{b6}
K. Czarnecki, P. Grünbacher, R. Rabiser, K. Schmid., and A.
Wasowski, “Cool features and tough decisions: a comparison of
variability modeling approaches”, Proc. of the \textit{Sixth international
workshop on variability modeling of software-intensive systems
(VaMoS '12)}, ACM, Jan 2012
\bibitem{b8} K. C. Kang, S. Cohen, J. Hess, W. Novak, and S. Peterson,	 "Feature oriented domain analysis (FODA) feasibility study", Technical Report CMU/SEI-90-TR-21, Software Engineering Institute, Carnegie Mellon University, Pittburgh, PA, USA, 1990
\bibitem{b9} A. Metzger, and K. Pohl, "Software product line engineering and variability management: Achievements and challenges," \textit{Proc. of the Future of Software Engineering (FOSE 2014)}, ACM, 2014, pp. 70-84, doi:10.1145/2593882.2593888.
\bibitem{b10} M. Riebisch, K. Böllert, D. Streitferdt, and I. Philippow, "Extending Feature Diagrams with UML Multiplicities", \textit{6th World Conference on Integrated Design \& Process Technology (IDPT2002)}, vol. 23, 2002
\bibitem{b11} K. Schmid, R. Rabiser, P. Grünbacher, "A comparison of decision modeling approaches in product lines", Proc. of the \textit{Fifth international
workshop on variability modeling of software-intensive systems
(VaMoS '11)}, ACM, Jan 2011
\end{thebibliography}
